### 2022-11-28 Paper2.Rmd
commit

---
title: "Paper 2, Econ 980x"
author: "Alice Chen"
date: "2022-11-27"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)

```

```{r files}

csv <- read_csv(file = "atus_00001.csv.gz") %>%
  clean_names()

# race 
race_file <- read_excel("race_980x.xlsx")

race_file <- race_file %>%
  rename(code1 = race) %>%
  rename(race = code)

csv <- left_join(csv, race_file, by = "race") %>%
  rename(race_code = race) %>%
  rename(race = code1)

# education
education_file <- read_excel("Education.xlsx")
education_file <- education_file %>%
  rename(code_educ = educ) %>%
  rename(educ = code_education) %>%
  mutate(educ = as.numeric(educ))

csv <- left_join(csv, education_file, by = "educ") %>%
  rename(code_education = educ) %>%
  rename(educ = code_educ)

# marital status
marital_file <- read_excel("marital_status.xlsx")
education_file <- marital_file %>%
  mutate(marst = as.numeric(marst))

csv <- left_join(csv, marital_file, by = "marst") %>%
  rename(code_marst = marst) %>%
  rename(marst = marst_code) %>%
  mutate(marst_simple = ifelse(code_marst <= 2, "Married", ifelse(code_marst >= 6, "Never Married", "Separated/Divorced")))

# age
csv <- csv %>%
  filter(age > 18)

# children
csv <- csv %>%
  mutate(child = ifelse(yngch < 19, 1, 0) )

# gender

csv <- csv %>%
  mutate(gender = ifelse(sex == 1, "male", "female"))

# years

```

```{r graphs}

#leisure hours aggregate
csv %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  labs(
  title = "Distribution of annual individual leisure hours",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

csv %>%
  filter(year %in% c(2007, 2009)) %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  facet_wrap(~year) +
  labs(
  title = "Distribution of annual individual leisure hours",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

#leisure hours aggregate by gender
csv %>%
  group_by(gender) %>%
  ggplot(mapping = aes(x = bls_leis) )+
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender) +
    labs(
  title = "Distribution of annual individual leisure hours by gender",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

csv %>%
  filter(year %in% c(2007, 2009)) %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender + year) +
  labs(
  title = "Distribution of annual individual leisure hours by gender",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

# Median
csv %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

# All Quantile
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
    facet_wrap(~ gender) +
  labs(
  title = "Annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

csv %>%
  group_by(year) %>%
  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
  ggplot(aes(x = year, y = hours, group = quantile)) +
  geom_line()

csv %>%
  group_by(year) %>%
  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile)) +
  geom_line()

# by year, gender
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
  facet_wrap(~gender) +
    labs(
  title = "Annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

# by year, gender
csv %>%
  group_by(year, gender) %>%
  summarize(median = median(bls_leis)) %>%
  clean_names() %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = median)) +
  geom_line() +
  facet_wrap(~gender) +
      labs(
  title = "Annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

#csv %>%
 # ggplot(mapping = aes(x = year, y = bls_leis)) + 
 # geom_jitter(alpha = 0.01)

```

```{r regressions, echo=FALSE}

#naive regression of men versus women

g <- csv %>%
  lm(formula = bls_leis ~ gender)

#naive regression of men versus women + year

y <- csv %>%
  lm(formula = bls_leis ~ gender + year)

# race count
newcsv <- csv %>%
 filter(race_code <= 210)

newcsv
newcsv %>%
  lm(formula = bls_leis ~ gender + year + age + race)

# 
a <- newcsv %>%
  lm(formula = bls_leis ~ gender + year + age + race) 
summary(a)

newcsv

# education
newcsv1 <- newcsv %>%
  mutate(new_educ = ifelse(code_education <= 17, "<High School", ifelse(code_education >= 40, ">Four Year Degree", "High School Graduate")))
  newcsv1

b <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ) 
summary(b)

newcsv1

# with children

c <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild) 
summary(c)

#marital status

d <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild + marst_simple) 
summary(d)

stargazer(g, y, a, title="Various Models", align=TRUE)
```

```{r moremodels}
#Change

change <- newcsv1 %>%
  group_by(gender,  year, new_educ, child, marst_simple) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change2 <- newcsv1 %>%
  group_by(gender, year) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change2

delta <- change %>%
  lm(formula = leisure_change ~ gender+ new_educ+ child+ marst_simple)
summary(delta)

```

### 2022-11-28 Paper2.Rmd
commit

@@
 library(stargazer)
+#library(tinytex)
 
@@
 
-stargazer(g, y, a, title="Various Models", align=TRUE)
+stargazer(g, y, a, title="Various Models", align=TRUE, type = "text")
 ```

### 2022-11-28 Paper2.Rmd
comit

@@
 output:
-  pdf_document: default
   html_document:
     df_print: paged
+  pdf_document: default
 ---
@@
 
-```{r regressions, echo=FALSE}
+```{r regressions}
 
@@
 
-stargazer(g, y, a, title="Various Models", align=TRUE, type = "text")
+stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
 ```
@@
 
-change2
+change3 <- newcsv1 %>%
+  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
+  summarize(median(bls_leis)) %>%
+  clean_names() %>%
+  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
+  clean_names() %>%
+  mutate(leisure_change = x2009 - x2007)
+
+#child
+newcsv1
 
@@
 
+delta3 <- change3 %>%
+  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
+summary(delta3)
+
 ```

### 2022-11-28 Paper2.Rmd
commit

@@
 #library(tinytex)
+library(ipumsr)
 
@@
 ```{r files}
+
+ddi <- read_ipums_ddi("atus_00005.dat")
+data <- read_ipums_micro(ddi)
 
@@
 # years
+
+csv %>%
+  summary(earnweek)
 
@@
 
+change4 <- newcsv1 %>%
+  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
+  summarize(mean(bls_leis)) %>%
+  clean_names() %>%
+  pivot_wider(values_from = mean_bls_leis, names_from = year) %>%
+  clean_names() %>%
+  mutate(leisure_change = x2009 - x2007)
+
 #child
 newcsv1
+
+delta <- change %>%
+  lm(formula = leisure_change ~ gender+ new_educ+ child+ marst_simple)
+summary(delta)
+
+delta4 <- change4 %>%
+  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
+summary(delta4)
+
+delta3 <- change %>%
+  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
+summary(delta3)
 
@@
 
+stargazer(delta, delta3, title="Models for Change in Leisure", align=TRUE, type = "text")
+
 ```

### 2022-11-28 Paper2.Rmd
commit

@@
 
-ddi <- read_ipums_ddi("atus_00005.dat")
-data <- read_ipums_micro(ddi)
+ddi <- read_ipums_ddi("atus_00005.xml")
+csv <- read_ipums_micro(ddi) %>%
+  clean_names()
 
-csv <- read_csv(file = "atus_00001.csv.gz") %>%
-  clean_names()
+data
+
+#csv <- read_csv(file = "atus_00001.csv.gz") %>%
+ # clean_names()
 
@@
   summary(earnweek)
+
+# employed
+csv <- csv %>%
+  mutate(empstat_cps8 = as.numeric(empstat_cps8)) %>%
+  mutate(emp = ifelse(empstat_cps8<= 2, "Employed", ifelse(empstat_cps8>=5, "Not In Labour Force", "Unemployed")))
 
@@
 ```
+```{r employment}
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(year) %>%
+  count(emp) %>%
+  filter(emp == "Unemployed") %>%
+  ggplot(mapping = aes(x = year, y = n)) +
+  geom_line() 
+  #facet_wrap(~emp)
+
+newcsv1 %>%
+  ggplot(mapping = aes(x = bls_leis)) +
+  geom_histogram() +
+  facet_wrap(~emp)
+
+newcsv1 %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median = median(bls_leis)) %>%
+  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
+  geom_line() +
+  facet_wrap(~gender + emp) +
+  labs(
+  title = "Distribution of annual individual leisure hours",
+  y = "Annual Hours",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median = median(bls_leis)) %>%
+  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
+  geom_line() +
+  facet_wrap(~gender + emp) +
+  labs(
+  title = "Distribution of annual individual leisure hours",
+  y = "Annual Hours",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+
+```
 

### 2022-11-28 Paper2.Rmd
commit

--- 2022-11-28 Paper2.Rmd
@@
 
+# Median 
+csv %>%
+  filter(year > 2005) %>%
+  filter(year < 2011) %>%
+  group_by(year, gender) %>%
+  summarize(median(bls_leis)) %>%
+  clean_names() %>%
+  ggplot(aes(x = year, y = median_bls_leis)) +
+  geom_line() +
+  facet_wrap(~ gender) +
+  labs(
+  title = "Median annual individual leisure hours by gender",
+  y = "Annual Hours",
+  x = "Year",
+  caption = "Data from ATUS",
+)
+
+# Mean
+csv %>%
+  filter(year > 2005) %>%
+  filter(year < 2011) %>%
+  group_by(year, gender) %>%
+  summarize(mean(bls_leis)) %>%
+  clean_names() %>%
+  ggplot(aes(x = year, y = mean_bls_leis)) +
+  geom_line() +
+  facet_wrap(~ gender) +
+  labs(
+  title = "Mean annual individual leisure hours by gender",
+  y = "Annual Hours",
+  x = "Year",
+  caption = "Data from ATUS",
+)
+
 # All Quantile
@@
   pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
-  filter(year > 2006) %>%
+  filter(year > 2005) %>%
   filter(year < 2011) %>%
@@
 ```
+```{r employment}
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(year) %>%
+  count(emp) %>%
+  filter(emp == "Unemployed") %>%
+  ggplot(mapping = aes(x = year, y = n)) +
+  geom_line() +
+  labs(
+  title = "Unemployment",
+  y = "Annual Hours",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+  #facet_wrap(~emp)
+
+newcsv1 %>%
+  ggplot(mapping = aes(x = bls_leis)) +
+  geom_histogram() +
+  facet_wrap(~emp)
+
+newcsv1 %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median = median(bls_leis)) %>%
+  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
+  geom_line() +
+  facet_wrap(~gender + emp) +
+  labs(
+  title = "Annual individual leisure hours",
+  y = "Annual Hours",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median = median(bls_leis)) %>%
+  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
+  geom_line() +
+  facet_wrap(~gender + emp) +
+  labs(
+  title = "Annual individual leisure hours",
+  y = "Annual Hours",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(emp, gender) %>%
+  tally()
+
+```
+
+```{r population_of_employment}
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(emp, year) %>%
+  tally() %>%
+  pivot_wider(names_from = year, values_from = n) %>%
+  clean_names() %>%
+  mutate(change_2008 = x2008-x2007) %>%
+  mutate(change_2009 = x2009-x2008) %>%
+  mutate(change_2010 = x2010-x2009) %>%
+  select(1, 6:8)
+
+```
 
@@
   group_by(gender,  year, new_educ, child, marst_simple) %>%
+  summarize(median(bls_leis)) %>%
+  clean_names() %>%
+  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
+  clean_names() %>%
+  mutate(leisure_change = x2009 - x2007)
+
+change11 <- newcsv1 %>%
+  group_by(gender,  year, new_educ, child, marst_simple, emp) %>%
   summarize(median(bls_leis)) %>%
@@
 
+change12 <- newcsv1 %>%
+  group_by(gender,  year, emp) %>%
+  summarize(median(bls_leis)) %>%
+  clean_names() %>%
+  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
+  clean_names() %>%
+  mutate(leisure_change = x2009 - x2007)
+
 #child
@@
 summary(delta)
+
+delta11 <- change11 %>%
+  lm(formula = leisure_change ~ gender+ new_educ+ child+ marst_simple + emp)
+summary(delta11)
+
+delta12 <- change12 %>%
+  lm(formula = leisure_change ~ gender + emp)
+summary(delta12)
 
@@
 ```
+
+```{r}
+
+```

### 2022-12-09 Paper2.Rmd
commit

@@
   labs(
-  title = "Distribution of annual individual leisure hours",
-  x = "Annual Hours",
+  title = "Distribution of daily individual leisure minutes",
+  x = "Daily Minutes",
   y = "Count",
@@
     labs(
-  title = "Distribution of annual individual leisure hours by gender",
-  x = "Annual Hours",
+  title = "Distribution of daily individual leisure minutes",
+  x = "Daily Minutes",
   y = "Count",
@@
   labs(
-  title = "Distribution of annual individual leisure hours by gender",
-  x = "Annual Hours",
+  title = "Distribution of daily individual leisure minutes",
+  x = "Daily Minutes",
   y = "Count",
@@
   labs(
-  title = "Median annual individual leisure hours by gender",
-  y = "Annual Hours",
+  title = "Median daily individual leisure minutes by gender",
+  y = "Daily Minutes",
   x = "Year",
@@
   labs(
-  title = "Mean annual individual leisure hours by gender",
-  y = "Annual Hours",
+  title = "Mean daily individual leisure minutes by gender",
+  y = "Daily Minutes",
   x = "Year",
@@
   labs(
-  title = "Annual individual leisure hours by gender",
-  y = "Annual Hours",
+  title = "Daily individual leisure minutes by gender",
+  y = "Daily Minutes",
   x = "Year",
@@
     labs(
-  title = "Annual individual leisure hours by gender",
-  y = "Annual Hours",
+  title = "Daily individual leisure minutes by gender",
+  y = "Daily Minutes",
   x = "Year",
@@
       labs(
-  title = "Annual individual leisure hours by gender",
-  y = "Annual Hours",
+  title = "Daily individual leisure minutes by gender",
+  y = "Daily Minutes",
   x = "Year",
@@
   title = "Unemployment",
-  y = "Annual Hours",
+  y = "Daily Minutes",
   x = "Count",
@@
   labs(
-  title = "Annual individual leisure hours",
-  y = "Annual Hours",
+  title = "Daily individual leisure minutes",
+  y = "Daily Minutes",
   x = "Count",

### 2022-12-09 Paper2.Rmd
commit

@@
 
-```{r files}
+```{r cashe data, cache = TRUE}
 
@@
   clean_names()
+
+```
+
+```{r files}
 
@@
   mutate(emp = ifelse(empstat_cps8<= 2, "Employed", ifelse(empstat_cps8>=5, "Not In Labour Force", "Unemployed")))
+
+# race
+csv %>%
+  count(race, sort = TRUE) %>%
+  filter(n > 1000)
+
+#We can see that top 5 groups > 1000 people
+
+csv <- csv %>%
+  filter(race %in% c("White only", "Black only", "Asian only", "American Indian, Alaskan Native", "White-American Indian"))
 
@@
 
-delta3 <- change %>%
+delta3 <- change4 %>%
   lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
@@
 
-```{r}
+```{r time-year-gender effects}
+
+summary(newcsv1)
+
+time_model <- newcsv1 %>%
+  lm(formula = bls_leis ~ gender*year + age + race*new_educ)
+
+summary(time_model)
 

### 2022-12-09 Paper2.Rmd
commit

@@
 time_model <- newcsv1 %>%
-  lm(formula = bls_leis ~ gender*year + age + race*new_educ)
+  mutate(year = as.character(year)) %>%
+  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ )
 
@@
 
+# W employment
+time_model1 <- newcsv1 %>%
+  mutate(year = as.character(year)) %>%
+  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp)
+
+summary(time_model1)
+
+newcsv1
+
 ```

### 2022-12-10 Paper2.Rmd
commit

@@
 library(stargazer)
-#library(tinytex)
+library(tinytex)
 library(ipumsr)
@@
 
+# W emp*gender
+time_model2 <- newcsv1 %>%
+  mutate(year = as.character(year)) %>%
+  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp*year)
+
+summary(time_model2)
+
 newcsv1
@@
 ```
+
+```{r tables, results = "asis"}
+
+stargazer(time_model, time_model1, time_model2, title="Models for Change in Leisure", align=TRUE, type = "html")
+
+```

### 2022-12-12 Paper2.Rmd
commit

@@
 library(ipumsr)
+library(dplyr)
+library(haven)
+library(survey)
+library(spatstat)
 
@@
 
+view(c)
 ```
@@
 csv %>%
+  filter(year < 2020) %>%
   group_by(gender) %>%
@@
 csv %>%
-  group_by(year, gender) %>%
-  summarize(median(bls_leis)) %>%
+  filter(year < 2020) %>%
+  group_by(gender, year) %>%
+  summarize(median_leisure = weighted.median(bls_leis, as.numeric(wt06), na.rm=TRUE)) %>%
   clean_names() %>%
-  ggplot(aes(x = year, y = median_bls_leis)) +
+  ggplot(aes(x = year, y = median_leisure)) +
   geom_line() +
@@
   title = "Median daily individual leisure minutes by gender",
+  y = "Daily Minutes",
+  x = "Year",
+  caption = "Data from ATUS",
+)
+
+# mean
+csv %>%
+  filter(year < 2020) %>%
+  group_by(gender,year) %>%
+  summarize(new = weighted.mean(bls_leis, wt06)) %>%
+  clean_names() %>%
+  ggplot(aes(x = year, y = new)) +
+  geom_line() +
+  facet_wrap(~ gender) +
+  labs(
+  title = "Weighted mean daily individual leisure minutes by gender",
   y = "Daily Minutes",
@@
   group_by(year, gender) %>%
-  summarize(median(bls_leis)) %>%
+  summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
   clean_names() %>%
@@
   labs(
-  title = "Median daily individual leisure minutes by gender",
+  title = "Weighted median daily individual leisure minutes by gender",
   y = "Daily Minutes",
@@
   group_by(year, gender) %>%
-  summarize(mean(bls_leis)) %>%
+  summarize(mean_bls_leis = weighted.mean(bls_leis, wt06)) %>%
   clean_names() %>%
@@
 csv %>%
+  filter(year < 2020) %>%
   group_by(year, gender) %>%
-  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
+  summarize(quantile_25 = weighted.quantile(bls_leis, wt06, prob = 0.25), quantile_50 = weighted.quantile(bls_leis, wt06, prob = 0.50), quantile_75 = weighted.quantile(bls_leis, wt06, prob = 0.75)) %>%
   clean_names() %>%
@@
   labs(
-  title = "Daily individual leisure minutes by gender",
+  title = "Weighted daily individual leisure minutes by gender",
   y = "Daily Minutes",
@@
 
-csv %>%
-  group_by(year) %>%
-  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
-  clean_names() %>%
-  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
-  ggplot(aes(x = year, y = hours, group = quantile)) +
-  geom_line()
-
-csv %>%
-  group_by(year) %>%
-  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
-  clean_names() %>%
-  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
-  filter(year > 2005) %>%
-  filter(year < 2011) %>%
-  ggplot(aes(x = year, y = hours, group = quantile)) +
-  geom_line()
-
 # by year, gender
 csv %>%
+  filter(year < 2020) %>%
   group_by(year, gender) %>%
-  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
+  summarize(quantile_25 = weighted.quantile(bls_leis, wt06, prob = 0.25), quantile_50 = weighted.quantile(bls_leis, wt06, prob = 0.50), quantile_75 = weighted.quantile(bls_leis, wt06, prob = 0.75)) %>%
   clean_names() %>%
@@
     labs(
-  title = "Daily individual leisure minutes by gender",
+  title = "Weighted daily individual leisure minutes by gender",
   y = "Daily Minutes",
@@
 g <- csv %>%
-  lm(formula = bls_leis ~ gender)
+  lm(formula = bls_leis ~ gender, weight = wt06)
+summary(g)
 
@@
 y <- csv %>%
-  lm(formula = bls_leis ~ gender + year)
+  lm(formula = bls_leis ~ gender + year, weight = wt06)
 
@@
 newcsv %>%
-  lm(formula = bls_leis ~ gender + year + age + race)
+  lm(formula = bls_leis ~ gender + year + age + race, weight = wt06)
 
@@
 a <- newcsv %>%
-  lm(formula = bls_leis ~ gender + year + age + race) 
+  lm(formula = bls_leis ~ gender + year + age + race, weight = wt06) 
 summary(a)
@@
 b <- newcsv1 %>%
-  lm(formula = bls_leis ~ gender + year + age + race + new_educ) 
+  lm(formula = bls_leis ~ gender + year + age + race + new_educ, weight = wt06) 
 summary(b)
@@
 c <- newcsv1 %>%
-  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild) 
+  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild, weight = wt06) 
 summary(c)
@@
 d <- newcsv1 %>%
-  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild + marst_simple) 
+  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild + marst_simple, weight = wt06) 
 summary(d)
@@
 ```
+
 ```{r employment}

### 2022-12-12 Paper2.Rmd
commit

@@
 library(spatstat)
+library(kableExtra)
+library(lfe)
 
@@
   mutate(new_educ = ifelse(code_education <= 17, "<High School", ifelse(code_education >= 40, ">Four Year Degree", "High School Graduate")))
-  newcsv1
 
@@
 summary(b)
-
-newcsv1
 
@@
 
-stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
+```
+
+```{r table0, results = "asis"}
+stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "html")
 ```
@@
   geom_histogram() +
-  facet_wrap(~emp)
+  facet_wrap(~emp) +
+  labs(
+  title = "Daily individual leisure minutes by employment type",
+  y = "Count",
+  x = "Daily Minutes",
+  caption = "Data from ATUS",
+)
 
 newcsv1 %>%
+  filter(year < 2020) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median = weighted.median(bls_leis, wt06)) %>%
+  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
+  geom_line() +
+  facet_wrap(~gender + emp) +
+  labs(
+  title = "Weighted daily individual leisure minutes",
+  y = "Daily Minutes",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year < 2020) %>%
   group_by(emp, gender, new_educ, year) %>%
@@
   title = "Daily individual leisure minutes",
+  y = "Daily Minutes",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median = weighted.median(bls_leis, wt06)) %>%
+  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
+  geom_line() +
+  facet_wrap(~gender + emp) +
+  labs(
+  title = "Weighted daily individual leisure minutes",
   y = "Daily Minutes",
@@
 
-newcsv1 %>%
+count_table <- newcsv1 %>%
   filter(year > 2006) %>%
@@
   tally()
+
+count_table2 <- newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2011) %>%
+  group_by(emp, gender, new_educ) %>%
+  tally()
+
+kable(count_table2) %>% kable_styling()
+kable(count_table) %>% kable_styling()
 
@@
   mutate(change_2010 = x2010-x2009) %>%
-  select(1, 6:8)
+  select(1, 6:8) %>%
+  kbl() %>%
+  kable_styling()
 
@@
 change <- newcsv1 %>%
+  filter(year<2020) %>%
   group_by(gender,  year, new_educ, child, marst_simple) %>%
-  summarize(median(bls_leis)) %>%
+  summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
   clean_names() %>%
@@
 change11 <- newcsv1 %>%
+  filter(year<2020) %>%
   group_by(gender,  year, new_educ, child, marst_simple, emp) %>%
-  summarize(median(bls_leis)) %>%
+   summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
   clean_names() %>%
@@
 change2 <- newcsv1 %>%
+  filter(year<2020) %>%
   group_by(gender, year) %>%
-  summarize(median(bls_leis)) %>%
+  summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
   clean_names() %>%
@@
 change3 <- newcsv1 %>%
+  filter(year<2020) %>%
   group_by(gender,  year, new_educ, nchild, marst_simple) %>%
-  summarize(median(bls_leis)) %>%
+   summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
   clean_names() %>%
@@
 change4 <- newcsv1 %>%
+  filter(year<2020) %>%
   group_by(gender,  year, new_educ, nchild, marst_simple) %>%
@@
 change12 <- newcsv1 %>%
+  filter(year<2020) %>%
   group_by(gender,  year, emp) %>%
-  summarize(median(bls_leis)) %>%
+   summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
   clean_names() %>%
@@
 
-stargazer(delta, delta3, title="Models for Change in Leisure", align=TRUE, type = "text")
+```
+
+```{r table1, , results = "asis"}
+stargazer(delta, delta3, title="Models for Change in Leisure", align=TRUE, type = "html")
 
@@
 
-summary(newcsv1)
+# First Set
 
 time_model <- newcsv1 %>%
+  filter(year < 2020) %>%
   mutate(year = as.character(year)) %>%
-  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ )
-
-summary(time_model)
+  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ,weights = wt06 )
 
@@
 time_model1 <- newcsv1 %>%
+  filter(year < 2020) %>%
   mutate(year = as.character(year)) %>%
-  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp)
-
-summary(time_model1)
+  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp, weights = wt06)
 
 # W emp*gender
+
 time_model2 <- newcsv1 %>%
+  filter(year < 2020) %>%
   mutate(year = as.character(year)) %>%
-  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp*year)
-
-summary(time_model2)
-
-newcsv1
+  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp + emp*year, weights = wt06)
 
@@
 
-```{r tables, results = "asis"}
+```{r table2, results = "asis"}
 
@@
 
+#stargazer(time_modela, time_model1a, time_model2a8, title="Models for Change in Leisure", align=TRUE, type = "html")
 ```
+
+```{r}
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  summarize(median_bls_leis_arts = weighted.median(bls_leis_arts, wt06),
+            median_bls_leis_attend = weighted.median(bls_leis_attend, wt06),
+            median_bls_leis_attsport = weighted.median(bls_leis_attsport, wt06),
+            median_bls_leis_partsport = weighted.median(bls_leis_partsport, wt06),
+            median_bls_leis_relax = weighted.median(bls_leis_relax, wt06),
+            median_bls_leis_soc = weighted.median(bls_leis_soc, wt06),
+            median_bls_leis_sport = weighted.median(bls_leis_sport, wt06),
+            median_bls_leis_soccom = weighted.median(bls_leis_arts, wt06),
+            median_bls_leis_travel = weighted.median(bls_leis_travel, wt06),
+            median_bls_leis_tv = weighted.median(bls_leis_tv, wt06)) %>%
+  pivot_longer(cols = everything(), names_to = "Activity", values_to = "Median Weighted Daily Minutes") %>%
+  kbl() %>%
+  kable_styling()
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
+            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
+            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
+            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
+            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
+            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
+            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
+            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
+  pivot_longer(cols = everything(), names_to = "Activity", values_to = "Mean Weighted Daily Minutes") %>%
+  kbl() %>%
+  kable_styling()
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  group_by(gender) %>%
+  summarize(median_bls_leis_arts = weighted.median(bls_leis_arts, wt06),
+            median_bls_leis_attend = weighted.median(bls_leis_attend, wt06),
+            median_bls_leis_attsport = weighted.median(bls_leis_attsport, wt06),
+            median_bls_leis_partsport = weighted.median(bls_leis_partsport, wt06),
+            median_bls_leis_relax = weighted.median(bls_leis_relax, wt06),
+            median_bls_leis_soc = weighted.median(bls_leis_soc, wt06),
+            median_bls_leis_sport = weighted.median(bls_leis_sport, wt06),
+            median_bls_leis_soccom = weighted.median(bls_leis_arts, wt06),
+            median_bls_leis_travel = weighted.median(bls_leis_travel, wt06),
+            median_bls_leis_tv = weighted.median(bls_leis_tv, wt06)) %>%
+  pivot_longer(!gender, names_to = "Activity", values_to = "Median Weighted Daily Minutes") %>%
+  kbl() %>%
+  kable_styling()
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median_bls_leis_arts = weighted.median(bls_leis_arts, wt06),
+            median_bls_leis_attend = weighted.median(bls_leis_attend, wt06),
+            median_bls_leis_attsport = weighted.median(bls_leis_attsport, wt06),
+            median_bls_leis_partsport = weighted.median(bls_leis_partsport, wt06),
+            median_bls_leis_relax = weighted.median(bls_leis_relax, wt06),
+            median_bls_leis_soc = weighted.median(bls_leis_soc, wt06),
+            median_bls_leis_sport = weighted.median(bls_leis_sport, wt06),
+            median_bls_leis_soccom = weighted.median(bls_leis_arts, wt06),
+            median_bls_leis_travel = weighted.median(bls_leis_travel, wt06),
+            median_bls_leis_tv = weighted.median(bls_leis_tv, wt06)) %>%
+  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
+  geom_line() +
+  facet_wrap(~gender + emp) +
+  labs(
+  title = "Daily individual leisure minutes",
+  y = "Daily Minutes",
+  x = "Count",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(median_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
+            median_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
+            median_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
+            median_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
+            median_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
+            median_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
+            median_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
+            median_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
+            median_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
+            median_bls_leis_tv = weighted.mean(bls_leis_tv, wt06))
+
+# TV Mean by Group   
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
+            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
+            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
+            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
+            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
+            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
+            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
+            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
+  ggplot(mapping = aes(x = mean_bls_leis_tv, y = emp, colour = new_educ)) +
+  geom_point() +
+  facet_wrap(~ gender + new_educ) +
+    labs(
+  title = "Average minutes individuals spend on watching TV",
+  y = "Employment Status",
+  x = "Daily Minutes",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
+            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
+            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
+            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
+            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
+            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
+            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
+            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
+  ggplot(mapping = aes(x = mean_bls_leis_relax, y = emp, colour = new_educ)) +
+  geom_point() +
+  facet_wrap(~ gender + new_educ) +
+  labs(
+  title = "Average minutes individuals spend on relaxation",
+  y = "Employment Status",
+  x = "Daily Minutes",
+  caption = "Data from ATUS",
+)
+
+newcsv1 %>%
+  filter(year > 2006) %>%
+  filter(year < 2009) %>%
+  group_by(emp, gender, new_educ, year) %>%
+  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
+            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
+            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
+            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
+            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
+            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
+            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
+            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
+            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
+  ggplot(mapping = aes(x = mean_bls_leis_soc, y = emp, colour = new_educ)) +
+  geom_point() +
+  facet_wrap(~ gender + new_educ) +
+  labs(
+  title = "Average minutes individuals spend on socializing",
+  y = "Employment Status",
+  x = "Daily Minutes",
+  caption = "Data from ATUS",
+)
+
+```
